---
title: "Lab 00 - Hello IDS!"
author: "Yanyi Chen"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Yanyi Chen", "Ziwei Huang", "Cathy Li", 
           "Nanshuyuan Zhang"),
  github_username = c("yanyi-c", "vivizhere", "Cathy0804", 
                      "znsy1219"), 
  colour = c("green", "blue", "red", 
             "green"),
  hobby = c("drama", "drawing", "baldursgate", 
            "computer games"),
  favourite_number = c(7, 8, 10, 6)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


*A plot for the favorite colors and favorite numbers of the four users*

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "github_username", 
          y = "favourite_number",
          title = "favorite_number/user")
```

*A plot for the favorite colors and favorite numbers of the four users*

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*A bar chart for the count of the four users' hobbies*
